Testing and Isolation Efficacy:\\Insights from a Simple Epidemic Model

### 2021-07-21 manuscript_BMB.tex
cover letter upd

DJDE, JD, and BMB were funded by the Natural Sciences and Engineering
Research Council of Canada, the Michael G. DeGroote Institute for Infectious
Disease Research at McMaster University, and the Public Health Agency of
Canada.

@@

Source code required to reproduce all analyses presented in this study are available at https://github.com/aligharouni/SIRmodel.

>>>>

(?) DJDE, JD, and BMB were funded by the Natural Sciences and Engineering
Research Council of Canada, the Michael G. DeGroote Institute for Infectious
Disease Research at McMaster University, and the Public Health Agency of
Canada.

@@

Source code required to reproduce all analyses presented in this study are available at \url{https://github.com/aligharouni/SIRmodel}.
